### 2016-08-29 version0.0/paper2.tex
Submitted version
Applying P.W.'s comments on ch.4

            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
            As in to Fig.~\ref{fig: sample_SOMZ}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
            As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
            The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                    \includegraphics[width=0.8\textwidth]{../image_paper2/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                     \includegraphics[width=0.8\textwidth]{../image_paper2/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption[Results of training network in $1\times2$~grid]{Results of training network in $1\times2$~grid. As in Fig.~\ref{fig: sample_SOMZ}, the upper panel is a distance map and the lower panel is a hit map. In this network, 5 of the templates from \citet{Kinney96} are categorized as quiescent galaxies and the rest are starbursts. Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

@@

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorize in a maximum 3 groups. 
            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups,
            while the white colour shows that the two right neurons are very similar to one another.

@@

        \subsubsection{Classifying the Galaxy Sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
            The lower left panel shows the average SED of the 80 galaxies that were classified as early type 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the SEDs clearly show the 4000\AA~break, one of the signatures of early type galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
            The average SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../image_paper2/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~networks]{Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies. Lower panel: Average SED of the galaxies in each group, early-type on the left and starburst on the right.}
                \label{fig: 1by2V}
            \end{figure}

@@

    \begin{figure}
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/2d/dist_12_by_12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/2d/dist_12_by_self_org_res12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/2d/hit_v_12_by_12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/2d/hit_v_12_by_self_org_res12.png}
        \end{subfigure}
        \caption[$12\times12$ two-dimensional self-organizing map results]{$12\times12$~2D SOM results. Upper pabel: SOMs trained using the \citet{Kinney96} templates. For training 2D SOMs two different approaches were considered: either only 12 types of galaxies exist (left) or not (right). Lower panel: classifying the galaxies from \citetalias{Hossein12}, using the trained networks shown in the upper panels. From the lower right panel, we can see that there are no outliers in the galaxies from \citetalias{Hossein12}, and we can use the map in the lower left panel as a final clustering result for the \citetalias{Hossein12} galaxies.}
        \label{fig: 12by12}
    \end{figure}

>>>>

            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
            As in to Fig.~\ref{fig: sample_SOMZ}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
            As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
            The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                  \includegraphics[width=0.8\textwidth]{../image_paper2/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                    \centering \includegraphics[width=0.8\textwidth]{../image_paper2/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption[Results of training network in $1\times2$~grid]{Results of training network in $1\times2$~grid. As in Fig.~\ref{fig: sample_SOMZ}, the upper panel is a distance map and the lower panel is a hit map. In this network, 5 of the templates from \citet{Kinney96} are categorized as quiescent galaxies and the rest are starbursts. Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

@@

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorized in a maximum 3 groups. 
            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups,
            while the white colour shows that the two right neurons are very similar to one another.

@@

        \subsubsection{Classifying the Galaxy Sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
            The lower left panel shows the average SED of the 80 galaxies that were classified as early type. 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the SEDs clearly show the 4000\AA~break, one of the signatures of early type galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
            The average SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../image_paper2/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~networks]{Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies. Lower panel: Average SED of the galaxies in each group, early-type on the left and starburst on the right.}
                \label{fig: 1by2V}
            \end{figure}

@@

    \begin{figure}
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/2d/dist_12_by_12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/2d/dist_12_by_self_org_res12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/2d/hit_v_12_by_12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/2d/hit_v_12_by_self_org_res12.png}
        \end{subfigure}
        \caption[$12\times12$ two-dimensional self-organizing map results]{$12\times12$~2D SOM results. Upper panel: SOMs trained using the \citet{Kinney96} templates. For training 2D SOMs two different approaches were considered: either only 12 types of galaxies exist (left) or not (right). Lower panel: classifying the galaxies from \citetalias{Hossein12}, using the trained networks shown in the upper panels. From the lower right panel, we can see that there are no outliers in the galaxies from \citetalias{Hossein12}, and we can use the map in the lower left panel as a final clustering result for the \citetalias{Hossein12} galaxies.}
        \label{fig: 12by12}
    \end{figure}
